Local Search, Brute-Force and Recursion for Selection Operator\thanks{This work was not supported by Velbazhd Software LLC and Bulgarian Ministry of Education and Science.}

### 2020-04-14 Local-Search-Brute-Force-and-Recursion-for-Selection-Operator/paper.tex
One space more.

\bibitem{wang-01} Q.Wang, ``The Genetic Algorithm and Its Application to Calibrating Conceptual Rainfall‐Runoff Models,'' {\it in Water Resoruces Research,} vol.~27, no.~9, 1991.

>>>>

\bibitem{wang-01} Q. Wang, ``The Genetic Algorithm and Its Application to Calibrating Conceptual Rainfall‐Runoff Models,'' {\it in Water Resoruces Research,} vol.~27, no.~9, 1991.
